%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Jakob Jakobsen}{Boysen}
\title{Ambitious software engineer}                               % optional, remove / comment the line if not wanted
\address{Reverdilsgade 7, 1. th}{DK-1701 København V}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+45 51 84 88 38}                   % optional, remove / comment the line if not wanted
\email{jakob@jboysen.dk}                               % optional, remove / comment the line if not wanted
%\homepage{www.jboysen.dk}
\extrainfo{\link{www.jboysen.dk}\\\link{www.github.com/jboysen}\\\link{www.linkedin.com/in/jakobboysen}}
% optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{UserPicture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2011--2014}{M.Sc.Eng. in Computer Science and Engineering}{Technical University of Denmark, DTU}{}{}{}  % arguments 3 to 6 can be left empty
\cventry{2008--2011}{B.Sc. in Computer Science}{Aarhus University}{}{}{}
\cventry{2004--2007}{STX, Mathematical}{Alssundgymnasiet Sønderborg}{}{}{}

\section{Relevant job experience}
\cventry{2013}{App developer}{Roskilde Festival}{Copenhagen}{}{Developed a streaming app for Roskilde Festivalradio. Both for Android and iOS.}
\cventry{2011--2013}{Student web developer}{Veloso A/S}{Hellerup}{}{Had the main responsibility for development and maintenance of the web application ActionPlanner\texttrademark. Development included working with PHP, MySQL, Python, Linux and Apache, with the MVC framework Symfony as the core of the product. Furthermore it also involved usage of the project management tool PivotalTracker and the support tool Zendesk.}
\cventry{2011--2013}{Partner}{CoolSoft I/S}{Copenhagen}{}{CoolSoft I/S was a company founded in collaboration with Morten Hulvej Andersen. The purpose of the company was to make it easy for us to take in smaller projects not related to our respective jobs.}
\cventry{2009--2011}{E-banking supporter}{Danske Bank}{Aarhus}{}{}
\cventry{2006--2007}{Tutor in Mathematics A}{Alssundgymnasiet}{Sønderborg}{}{}

%\section{Master Thesis}
%\cvitem{title}{\emph{Sentiment Analysis}}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}

\section{Relevant skills}
\cvitem{OOP}{Both professionally and academically I have used quite a few object-oriented programming languages and have a huge understanding of programming in general. \textbf{Java} has been used to many different courses and also to develop Android apps. \textbf{C\#} has been used to many different courses as well. \textbf{Objective-C} has been used to develop a few iOS apps. Object-oriented \textbf{PHP} has been used professionally for a year and a half. I have used \textbf{C} and \textbf{C++} to a smaller degree on smaller projects.}
\cvitem{OS}{I'm using Mac OS (based on UNIX) as primary OS.}
\cvitem{Other}{I have designed a DSL for the job-shop scheduling problem using \textbf{F\#}. I have played a bit around with \textbf{Javascript} (specifically \textbf{Node.js} in my spare time and the front-end framework \textbf{jQuery} professionally). I have been using and optimising \textbf{SQL}-queries professionally. \textbf{Python} has been used to solve minor tasks.}

\section{Languages}
\cvitemwithcomment{Danish}{Mother tongue}{}
\cvitemwithcomment{English}{Advanced}{Have been using English as primary language both professionally and academically.}
\cvitemwithcomment{German}{Beginner}{Can read and understand.}

\section{Personal information}
\cvitem{}{Born the 14th of May 1987. Grew up on a farm near Sønderborg. Went to boarding school at Bernstorffsminde Efterskole in 2003--2004. Moved to Aarhus to study computer science after having had a year off after high school, and moved to Copenhagen to pursue my master's degree at DTU by the fall of 2011.}
\cvitem{}{Love music, going to concerts, working out, software engineering and interested in what happens in the society around me.}






%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
